Solving the maximum independant set problem by generic programming einsum networks

### 2021-06-12 paper/paper.tex
update
demos

@@

\section{Utilizing sparsity}
So far, we have used the language of einsum networks for contraction.
When using sparse tropical tensor networks to find the maximum independent set, we can introduce a new rule to compress the tensor by removing elements that are not helpful.
As show in \Fig{fig:compressrule}, after we contract the tensors in a subregion $R \subseteq G$ of a graph $G$, and obtain a resulting tensor $A$ of rank $|C|$, where $C$ is the set of vertice tensors at the cut.
Each tensor entry $A_{\sigma}$ defines a local maximum independant set size with a fixed boundary configuration $\sigma \in \{0,1\}^{|C|}$ by marginalizing the inner degrees of freedom.
We call this properly the \textit{local maximum rule}.

@@

>>>>

\section{Introduction}
Exact algorithms that solves the MIS problem in $1.1893^n n ^{O(1)}$ time ~\cite{Xiao2017}.

@@

\section{Automated branching}
% check http://www.tcs.rwth-aachen.de/independentset/ for more rules
So far, we have used the language of einsum networks for contraction.
When using sparse tropical tensor networks to find the maximum independent set, we can introduce a new rule to compress the tensor by removing elements that are not helpful.
As show in \Fig{fig:compressrule}, after we contract the tensors in a subregion $R \subseteq G$ of a graph $G$, and obtain a resulting tensor $A$ of rank $|C|$, where $C$ is the set of vertice tensors at the cut.
Each tensor entry $A_{\sigma}$ defines a local maximum independant set size with a fixed boundary configuration $\sigma \in \{0,1\}^{|C|}$ by marginalizing the inner degrees of freedom.
We call this properly the \textit{local maximum rule}.

@@

\begin{table}[h!]\centering
\begin{minipage}{0.9\columnwidth}
\ra{1.3}
    \scalebox{1.0}{
        \begin{tabularx}{\textwidth}{bb}\toprule
            \hline
            \textbf{element type}     & \textbf{purpose} \\
            {regular number}     & {counting all indenepent sets} \\
            {tropical number}     & {finding the maximum independent set size} \\
            {tropical number with counting}     & {finding both the maximum independent set size and its degeneracy} \\
            {tropical number with configuration}     & {finding the maximum independent set size and one of the optimal configurations} \\
            {tropical number with multiple configurations}     & {finding the maximum independent set size and all optimal configurations} \\
            {polynomial}     & {computing the indenpendence polynomials exactly} \\
            {complex number}     & {fitting the indenpendence polynomials with fast fourier transformation} \\
            {finite field algebra}     & {fitting the indenpendence polynomials exactly using number theory} \\
            \bottomrule
        \end{tabularx}
    }
    \caption{Tensor element types used in the main text and their purposes.}\label{tbl:generictypes}
\end{minipage}
\end{table}
